\documentclass[a4paper,11pt]{article}

% --- PACKAGES & STYLING ---
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% --- COLORS ---
\definecolor{darkblue}{RGB}{0,0,139}

% --- PAGE SETUP ---
\setlength{\multicolsep}{0pt}
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{} 
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt}

% --- HYPERLINKS ---
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue
}

% --- SECTION HEADERS (tcolorbox) ---
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,
    outer arc=0pt
}

% --- TYPOGRAPHY & COMMANDS ---
\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

\newcommand{\resumeItem}[2]{\item{\textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}}}

\newcommand{\resumeSubheading}[4]{\vspace{0.5mm}\item
\begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & \textit{\footnotesize{#4}} \\
\textit{\footnotesize{#3}} & \footnotesize{#2}
\end{tabular*}\vspace{-2.4mm}}

\newcommand{\resumeProject}[4]{\vspace{0.5mm}\item
\begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & \textit{\footnotesize{#3}} \\
\footnotesize{\textit{#2}} & \footnotesize{#4}
\end{tabular*}\vspace{-2.4mm}}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=0.9mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.6mm]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{\vspace{2mm}\begin{tcolorbox}\textbf{\large #1}\end{tcolorbox}\vspace{-4mm}}

\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont}

\begin{document}
\headerfontiii

% --- HEADER ---
\begin{center}
    {\Huge\textbf{ADIL ALAMI}}
\end{center}
\vspace{-3mm}
\begin{center}
    \small{
    +212-608-255-560 \;|\; \href{mailto:adilalami707@gmail.com}{adilalami707@gmail.com} \;|\;
    \socialicon{\textcolor{blue}{\faLinkedin}} \href{https://www.linkedin.com/in/adil-alami/}{adil-alami} \;|\;
    \socialicon{\textcolor{darkblue}{\faGithub}} \href{https://github.com/Aeidle}{Aeidle} \;|\;
    Fez, Morocco}
\end{center}
\vspace{-4mm}

% --- SKILLS ---
\section{\textbf{Skills}}
\vspace{-0.4mm}
\resumeHeadingSkillStart
  \resumeSubItem{Programming:}{Python, C\#, C}
  \resumeSubItem{AI/ML:}{TensorFlow, PyTorch, scikit-learn, Pandas, NumPy, OpenCV}
  \resumeSubItem{Platforms \& Data:}{FastAPI, Django, AWS (S3, DynamoDB), OVH, MQTT, RabbitMQ, PostgreSQL, MongoDB, Cassandra, Spark, Kafka, Docker, Git, DVC, MLflow}
\resumeHeadingSkillEnd

% --- EXPERIENCE ---
\section{\textbf{Experience}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

  \resumeSubheading
  {Voicari}{Berlin, Germany (Remote)}
  {Freelance Data Scientist}{May 2025 – Present}
      \resumeItemListStart
        \item Built the core AI system and models, focusing on real-time emotion recognition from acoustic and physiological signals.
        \item Designed a distributed Big Data architecture: ingested IoT sensor data via \textbf{MQTT}, buffered high-throughput streams using \textbf{Kafka}, and managed asynchronous inference tasks with \textbf{RabbitMQ}.
        \item Deployed scalable backends with \textbf{Docker} on \textbf{AWS (S3, DynamoDB)} and \textbf{OVH}, ensuring reliable audio storage and real-time device state synchronization.
        \item Developed internal analytics dashboards and tools to visualize model performance and monitor system metrics.
      \resumeItemListEnd

  \resumeSubheading
      {Faculty of Sciences Agadir – Ibn Zohr University}{Agadir, Morocco}
      {AI Engineer — PFE Internship}{Mar 2025 – Jul 2025}
      \resumeItemListStart
        \item Built \textbf{OpenFirmaAI}: A smart greenhouse management platform (FastAPI backend, Next.js frontend).
        \item Developed deep learning models to predict water and fertigation needs for tomato crops, optimizing yield and resource usage.
        \item Integrated an LLM-based expert agent to interpret model predictions, providing farmers with human-readable context and agronomic recommendations.
      \resumeItemListEnd

  \resumeSubheading
      {WeHelp Group}{Meknes, Morocco}
      {Data Scientist — Intern}{Apr 2023 – Oct 2023}
      \resumeItemListStart
        \item Led \textbf{AEye}: An assistive navigation system for the visually impaired using YOLO object detection and DeepSort tracking.
        \item Developed \textbf{PlantAI}: An end-to-end plant disease recognition application using EfficientNet and Django.
      \resumeItemListEnd

  \resumeSubheading
      {ITRAV Engineering}{Fez, Morocco}
      {Freelance Web Developer}{Oct 2022 – Mar 2023}
      \resumeItemListStart
        \item Delivered responsive corporate websites using HTML5, CSS3, and JavaScript, ensuring cross-browser compatibility.
      \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}

% --- EDUCATION ---
\section{\textbf{Education}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{Ibn Zohr University}{Taroudant, Morocco}
{Master’s in Big Data and Artificial Intelligence — \textit{Valedictorian}}{Oct 2023 – Jul 2025}
\resumeItemListStart
\item Focus: Deep Learning, Data Engineering, Distributed Systems.
\resumeItemListEnd

\resumeSubheading
{Higher School of Technology}{Meknes, Morocco}
{B.A.S. in AI and Data Science — \textit{Valedictorian}}{Oct 2022 – Jun 2023}
\resumeItemListStart
\item Focus: Machine Learning, Data Analysis, Software Engineering.
\resumeItemListEnd

\resumeSubheading
{Higher School of Technology}{Meknes, Morocco}
{Associate Degree in Audiovisual Technologies — \textit{Distinction}}{Oct 2019 – Jun 2021}
\resumeItemListStart
\item Focus: Audio/Visual Systems, Digital Imaging.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}

% --- PROJECTS ---
\section{\textbf{Projects \& Publications}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
  {SavePip — Smart Dependency Management Tool}
  {Python, CLI, PyPI, Conda}
  {Present}
  {[\href{https://github.com/Aeidle/savepip}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Developed an open-source CLI tool to intelligently install and track packages, preventing \texttt{requirements.txt} bloat.
  \item Features include smart synchronization, category management (dev/prod), and support for both pip and conda.
  \item Published on PyPI; simplifies environment management by separating explicit dependencies from sub-dependencies.
\resumeItemListEnd

\resumeProject
  {OpenFirmaAI — Agricultural Management System (PFE)}
  {FastAPI, Python, Next.js, Seq2Seq, Mistral LLM}
  {Jul 2025}
  {[\href{https://github.com/Aeidle/OpenFirmaAI/blob/main/Poster\%20A0\_ADIL-ALAMI.pdf}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Greenhouse monitoring and predictive analytics system for tomato cultivation with LLM-based interpretability.
\resumeItemListEnd

\resumeProject
  {OpenVote — Decentralized Voting System}
  {Solidity, Ethereum, Smart Contracts, Next.js}
  {Apr 2025}
  {[\href{https://github.com/Aeidle/OpenVote}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Full-stack dApp featuring secure, audited smart contracts and a modern user interface.
\resumeItemListEnd

\resumeProject
  {Hespress Sentiment Analysis — Moroccan Darija (ICAMAI’25)}
  {Kafka, Spark, PostgreSQL, Cassandra, BiLSTM}
  {Feb 2025}
  {[\href{https://github.com/Aeidle/ICAMAI25_Communication/blob/main/ICAMAI-25_ADIL-ALAMI.pdf}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item End-to-end Big Data pipeline for sentiment analysis; presented at \textbf{ICAMAI 2025} (attestation available).
\resumeItemListEnd

\resumeProject
  {Tomato Sorting Line — Ripeness \& Size}
  {Python, OpenCV, CNN}
  {Feb 2025}
  {[\href{https://github.com/Aeidle/Tomato-Sorter}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item CNN-based computer vision model for automated grading on industrial production lines.
\resumeItemListEnd

\resumeProject
  {EAR Fatigue Detection — Real-time Drowsiness Monitoring}
  {Python, OpenCV, Dlib}
  {Feb 2024}
  {[\href{https://github.com/Aeidle/EAR-Fatigue-Detection}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
  \item Developed a computer vision system to detect student fatigue using Eye Aspect Ratio (EAR) and facial landmarks.
  \item Implemented real-time monitoring and alerting mechanisms to enhance safety and learning quality.
\resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-6mm}
\section{\textbf{Additional Information}}
\vspace{-0.4mm}
\small{
\textbf{Languages:} Arabic (Native), English (Proficient), French (Intermediate) \\
\textbf{Interests:} Coding, Chess, Video Games
}

\end{document}